Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-09-01 paper/manuscript.Rmd
add kable to manuscript
rm double output

---
title: Interisland movements and oceanic swimming of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
    ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial
   University of Newfoundland, Canada
    ^2^Department of Biology, Memorial University of Newfoundland, Canada
    #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output:
   github_document: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
bibliography: ../references/swim.bib
csl: ecology.csl
---

@@

>>>>

---
title: Interisland movements and oceanic swimming of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
    ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial
   University of Newfoundland, Canada
    ^2^Department of Biology, Memorial University of Newfoundland, Canada
    #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output:
   bookdown::word_document2:
     reference_docx: template.docx
bibliography: ../references/swim.bib
csl: ecology.csl
---

@@

```{r tab1}
knitr::kable(readRDS('../output/table1.Rds'),
             caption = '')
```
